---
title: "Text, Candles, and Dates"
description: |
  Data Collection
author:
  - name: Robert Hess
    url: {}
date: 05-19-2021
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load.libraries, include=FALSE}
library(tidyverse)
library(lubridate)
library(dygraphs)
```


# Data Collection

This project requires data from many different sources to be combined together. I needed to find and obtain raw text from the [Federal Reserve](https://www.federalreserve.gov/monetarypolicy/FOMC_historical_year.htm), Candle Data from [Oanda](www.oanda.com), and Dates and Times from [forexfactory](forexfactory.com).

### Federal Reserve & Forex Factory

In order to find which news events I wanted to use, I went through the [Forex Factory](forexfactory.com) and found one of the events on their calender. These FOMC Statements have a naming pattern on the Federal Reserve Website. They are marked by date. I found a list of dates for all of the statements that happened since 2007. I used python to download the HTMLs and then stripped the Statement text from the HTMLS using some simple regex.

### Oanda

Oanda can provide their candle data to those who have their API. I used a candle downloader from the company Liberty Dynamic Consultants in which I am a stakeholder and have access to their technology. Getting the Postgresql database setup on my computer had a few settings issues that made it difficult.


# Data Wrangling

### Regexes

**Look Aheads and Look Behinds**
This regex finds any "." or lowercase letter that is followed by an uppercase letter.
`([.a-z](?=[A-Z]))`
This regex finds 2 or more whitespaces together that have words ahead and digits behind.
`((?<![\d\s])\s\s+(?=\w))`

**Remove punct**
This regex finds all none word and none space and non "-" characters and deletes them.
`re.sub(r'[^\w\s-]', '', x)`


### Average True Range (ATR)

The ATR is the average amount that the market is moving. In order to calculate this take the high of a candle and subtract the low. Add this number to all the other high-low and divide by the number of candles. Example of doing this in R: `candles_with_atr_30_min <- candles_filtered %>%`
  `arrange(date) %>%`
  `mutate(row_num = row_number()) %>%`
  `rowwise() %>% `
  `mutate(atr = atr_calc(candles_filtered[(abs(row_num-14)):abs(row_num-1),3],`
  `candles_filtered[abs(row_num-14):abs(row_num-1),4]))`
  
`atr_calc <- function(high.df, low.df){ return(sum(high.df - low.df) / nrow(high.df)) }`

The ATR will be part of how we will be classifying the raw text.

